---
title: "Arrest Analysis"
author: "Jeff Allen"
date: "09/24/2014"
output: html_document
---

# Arrest Analysis of Lake County, CA

We've already downloaded the data (via `dataCollection.Rmd`) in the `data/` dir, so we'll load it in and take a look.

```{r}
library(lubridate)

arrests <- readRDS("data/arrests.Rds")
load("data/bookings.Rda")
# Produces `bookings` and `charges` objects.
```

In total, we have `r nrow(arrests)` arrests recorded with `r length(bookings)` bookings and `r length(charges)` charges on those bookings. These bookings range from `r format(min(arrests[,"Time Booked"]), "%B %d, %Y")` to `r format(max(arrests[,"Time Booked"]), "%B %d, %Y")`.

We can now check out a few properties about those arrested.

### Ethnicity

Using some simplified racial data from the 2011 census, we can compare those arrested vs. the demographics of Lake County.

```{r, fig.width=9}
# Demographics of Lake County
source("LakeCounty/demographics.R")
as.character(raceAbbrevs)
races


# Extract the race of everyone arrested
arrRac <- gsub("(\\w)\\/\\w", "\\1", arrests$`Race/Sex`)
# Set to "Other" if we don't know this race.
arrRac[!arrRac %in% names(raceAbbrevs)] <- "O"
emp <- table(arrRac)/length(arrRac)

# Compute the difference
delta <- emp - races[names(emp)]
names(delta) <- as.character(raceAbbrevs[names(delta)])
barplot(delta, ylab="Under-Represented      <-->      Over-Represented", main="Arrests by Race")
abline(h=0)
```

### Gender

Using some simplified racial data from the 2011 census, we can compare those arrested vs. the demographics of Lake County.

```{r, fig.width=9}
# Demographics of Lake County
gender <- unlist(gender)
gender

# Extract the gender of everyone arrested
arrGen <- gsub("\\w\\/(\\w)", "\\1", arrests$`Race/Sex`)
# Set to "Other" if we don't know this race.
arrGen[!arrGen %in% names(gender)] <- "O"
emp <- table(arrGen)/length(arrGen)

# Compute the difference
delta <- emp - gender[names(emp)]

names(delta) <- as.character(genAbbrev[names(delta)])
barplot(delta, ylab="Under-Represented      <-->      Over-Represented", main="Arrests by Gender")
abline(h=0)
```

### Age

We can do the same for age.

```{r, fig.width=9}
# Demographics of Lake County
names(ages) <- 1:length(ages)
# Normalize to a percentage (It should be close to start. Formalize it)
ages <- ages/sum(ages)


arrests$DOB <- mdy(arrests$DOB, tz="PDT")
span <- as.duration(new_interval(arrests$DOB, arrests$`Time Booked`))
# Convert to seconds
suppressWarnings(span <- as.integer(span))
# Convert to years -- age at time of arrest
span <- span/60/60/24/365.25

dens <- density(span, na.rm=TRUE)

# Plot arrests
plot(0,0, type="n", ylim=c(0,max(dens$y)), xlim=c(1,length(ages)), ylab="Arrests", xlab="Age at Time of Arrest", main="Arrests by Age")
lines(dens)

# Plot demographics
lo <- loess.smooth(1:length(ages), ages, span=.25, degree=1, family="symmetric", evaluation=100)
lines(lo, col=2)

legend(x=60, y=max(dens$y), legend=c("Arrests", "Population"), col=1:2, lwd=2)

```








