---
title: "Lake County Arrest Data Collection"
author: "Jeff Allen"
date: "09/24/2014"
output: html_document
---

## Data Collection

We'll first want to download the data. For starters, we can get the past year of arrests data.

```{r, getArrests, cache=TRUE}
# We'll need to source the supporting functions.
source("LakeCounty/demographics.R")
source("LakeCounty/getRecords.R")
source("LakeCounty/parseRecords.R")
source("Weather/DownloadHistoric.R")
source("Weather/getRecords.R")

# Make the data dir
dir.create("data", showWarnings = FALSE)

pastYear <- today()
year(pastYear) <- year(today())-3
days <- itemizeDates(startDate = pastYear, today())

# Get all the records, we'll pause for 1 second in between each to avoid overwhelming
# their server. So we expect this to take 6+ minutes.
arrests <- NULL
for (d in days){
  dat <- downloadDate(month(d), day(d), year(d))
  arrests <- rbind(arrests, dat)    
  Sys.sleep(1)
}

# Clean up the arrests$`Time Booked` field
tb <- arrests$`Time Booked`
tb <- as.character(tb)
# Restore a space
tb <- gsub("([\\d/]+)(\\d\\d:\\d\\d)","\\1 \\2",tb, perl=TRUE)
tb <- mdy_hm(tb, tz="PDT")
arrests$`Time Booked` <- tb

saveRDS(arrests, "data/arrests.Rds")
```

The real information is contained on a detail page within each booking, though. We'll have to get those individually which will take *much* more time since there are `r nrow(arrests)` arrests to collect. We have a helper function for this, though.

```{r, getBookingsAndCharges, cache=TRUE, results='hide'}
bookCharg <- getBookings(arrests[,1], outputFile="data/bookings.Rda")
charges <- bookCharg$charges
bookings <- bookCharg$bookings
```

Now we have all the arrests, bookings, and charges (and saved a copy to disk for later analysis).








